Analytics Without Parameter Tuning Considered Harmful?

### 2015-03-16 dm101.tex
Updates from ShareLaTeX

{\em Easy to use:} Static code attributes can be automatically collected, even for very large systems~\cite{nagappan05}.
Other methods, like  manual code reviews, are far slower and far more labor-intensive.
For example, depending on the review methods, 8 to 20 LOC/minute can be
inspected and this effort repeats for all members of the review team,
which can be as large as four or six~\cite{me02f}.

>>>>

{\em Easy to use:} Static code attributes can be automatically collected, even for very large systems~\cite{nagappan05}.
Other methods, like  manual code reviews, are far slower and far more labor-intensive.
For example, depending on the review methods, 8 to 20 LOC/minute can be
inspected and this effort repeats for all members of the review team,
which can be as large as four or six people~\cite{me02f}.

### 2015-03-16 learners.tex
Updates from ShareLaTeX

This section describes this study's learners: CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
and WHERE~\cite{menzies2013local}.
The implementations
for CART and Random Forest comes from 
SciKitLearn~\cite{scikit-learn}.
WHERE is available from
github.com/ai-se/where.

\fig{parameters} shows the tuning parameters of these learners.
WHERE has the most tuning parameters. This turns out
to be important since, in the experiments shown below, tuned WHERE 
out-performed the other learners-- a result suggesting that
if you are going to tune learners, then use one with many tuning options.

@@

From all the above methods, how do we select which optimizers to apply to tuning data miners.
Cohen~\cite{cohen95} advises comparing any supposedly more
sophisticated method against the simplest possible alternative. For
example, in one study with ``floor effects'', Holte showed that,
often, much of the performance of complex multi-level decision trees
could be easily achieved using a much simpler single-level decision
tree learner called 1R~\cite{holte93}. He therefore recommends a very simple rule learner
(called ``1R'') as a
kind of ``scout'' that can do a quick preliminary analysis of a data
set and which can report back if that data really requires a more
complex analysis.

>>>>

This section describes this study's learners: CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
and WHERE~\cite{menzies2013local}.
The implementations
for CART and Random Forest comes from 
SciKitLearn~\cite{scikit-learn}.
WHERE is available from
github.com/ai-se/where.
\fig{parameters} shows the tuning parameters of these learners.

@@

From all the above methods, how do we select which optimizers to apply to tuning data miners?
Cohen~\cite{cohen95} advises comparing any supposedly more
sophisticated method against the simplest possible alternative. For
example, in one study with ``floor effects'', Holte showed that,
often, much of the performance of complex multi-level decision trees
could be easily achieved using a much simpler single-level decision
tree learner called 1R~\cite{holte93}. He therefore recommends a very simple rule learner
(called ``1R'') as a
kind of ``scout'' that can do a quick preliminary analysis of a data
set and which can report back if that data really requires a more
complex analysis.

### 2015-03-16 tuningpredictor.tex
Updates from ShareLaTeX

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{ Analytics Without Parameter Tuning Considered Harmful?}
\numberofauthors{1}
\author{\alignauthor Wei Fu, Tim Menzies, Vivek Nair\\
       \affaddr{Computer Science, North Carolina State University, Raleigh, USA}\\
       fuwei.ee, tim.menzies, vivekaxl@gmail.com}
\maketitle
\begin{abstract}
One of the ``black arts'' of data mining is setting the tuning
parameters that control   choices within a data miner.  We offer a simple,
automatic, and very effective  method for finding those tunings.

@@

One of the ``black arts'' of data mining is setting the tuning
parameters that control  the choices within that data miner.
Many researchers have applied automatic optimizers to find good tunings.
The search-based SE community has   developed techniques
for tuning that treat parameters  as a configuration
search space~\cite{cora10,Krogmann10}. 
The field of {\em hyper-heuristics} explores methods for auto-adapting
options within the device searching for solutions~\cite{jia2013learning} in applications
like test-case generation and code refactorings.

To the best of our knowledge, this paper is the first extensive exploration 
of applying automatic optimizers to tune data miners for defect prediction,
(though see~\cite{cora10,balogh12,Minku13,minku13z} for tuning effort estimators).
The one similar study  we can find in the period 2004 to 2014\footnote{See the GECCO and SSBSE proceedings at    goo.gl/2MY602 and goo.gl/uzvU8e.} was
Bouktiff et al.~\cite{Bouktif06} who used  simulated annealing to tune Bayes classifiers.
That was a very limited study, applied to a  single defect data set.
The analysis of this paper is far more extensive and offers the following novel results:
\bi
\item
Tuning static code defect predictors is {\em remarkably simple} and can {\em dramatically improve the performance}
of those learners. 
\ei
Prior to these experiments, our expectation was tuning
would be an  extensive and expensive evolutionary optimization procedure. 
A standard run of such evolutionary optimizers requires   thousands,
if not millions, of evaluations.
To
our surprise, we achieved dramatic improvements in the performance scores
of our data miners after  mere 50 to 80 evaluations (!!) of a very simple evolutionary 
optimizer  called differential evolution~\cite{storn1997differential}.
Better yet,  those  tunings (found so quickly)   
  have a dramatic change to the performance of a learner. For example,
in this paper we show that tuning can alter the precision of
a software defect predictor from 2\% to 98\%.

@@

Thirdly, it is a standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
we have defended that approach on methodological grounds arguing that it
encourages reproducibility~\cite{me15:book1}). That ``off-the-shelf''  policy
can no longer be condoned. For example, one such default setting
  in the Python \mbox{SciKitLearn} toolkit~\cite{scikit-learn}
is to use $F=10$ decision trees in  Random Forest classifiers.
Our optimizer settled on  $F$ values that were nowhere near that default:

{\scriptsize
\[F \in \left\{\begin{array}{l} 55,  65, 70,   82, 88, 96, 100,  102,  104, 107,\\
                                108,  119, 133,  140, 140,   147,  145,  142   \end{array}\right\}
\]}

@@

@@

\noindent
We now explore how tuning can alter the above  conclusion. Suppose the  predictors $d_1$ and $d_2$  learned from LOC or Halstead
are used to call an inspection
team to check for errors in   parts of the code using:
\begin{equation}\label{eq:yesno}\scriptsize
\mathit{inspect}= \left\{
\begin{array}{ll}
d_i \ge T \rightarrow \mathit{Yes}\\
d_i <   T \rightarrow \mathit{No} 
\end{array}\right.
\end{equation}
\fig{pd1} shows the effects of tuning. Not surprisingly,
at $T=0$, all modules get inspected so the false alarm rate is very high. To reduce that
problem, we can increase $T$. \fig{pd1} reports that the false alarm rate falls below
20\% at $T=0.45$ (for Halstead).

@@

One   lesson from  \fig{pd1} is that the ``best'' tunings are context
specific. For mission critical systems (e.g. a nuclear power plant), management
might accept the cost of high false alarm rates if it meant increasing the probability
of detecting errors. For such contexts, we might recommend some very small value of $T$.

The other   lesson from   \fig{pd1}  is that, with tuning, a seemingly poor
detector can work just as well as seemingly better ones.
Note that either the Halstead or LOC detector can reach some desired
level of recall, regardless of their correlations, just by
selecting the appropriate threshold value. For example, in \fig{pd1}, see the recall=75\% values
found at {\em either} $d_i\ge 0.65$ or $d_2\ge 0.45$ (and at the threshold, the false alarm rates
were very similar: 14\% and 19\%).

@@

\section{Experimental Design}

@@

For this experiment, we use data sets with at least three  
consecutive releases  (where release $i+1$ was built after release $i$).
\bi 
\item The {\em first} release was used for some  {\em training}, to collect a baseline
   using an untuned learner. This release is also used  on line 24 of Algorithm~\ref{alg:DE} to
   build some model using some the tunings found in some {\em Candidate}.
   \item The {\em second} release was used on 25 of Algorithm~\ref{alg:DE} to 
   test the model found on line 24.
   \item Finally the {\em third} release was used to gather the performance statistics
   reported below from (a)~the model generated by the untuned learner or (b)~the
   best model found by differential evolution.
   \ei
This approach ensures   all treatments 
are assessed on the same tests.

@@

\begin{figure}[!b]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
One style
of measure is to check the {\em variability} of that predictor.
For example,
in their study on reproducibility of SE results,
 Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.

@@

In {\em Better-faster-cheaper},   project want changes that lead
to fewer defects,  faster development,  using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.

@@

{\scriptsize\[
\begin{array}{ll}
pd=recall=&D/(B+D)\\
pf=&C/(A+C)\\
pf'=& 1 - pf\\
prec=precision=&D/(D+C) 
\end{array}
\]}

All the above vary from zero to one. For $pf$, the {\em better} scores are {\em smaller}.
For all other scores, the {\em better} scores are {\em larger}.

The following results make no assumption that (e.g.) minimizing false alarms is 
more important than maximizing   precision. That determination 
depends on current business conditions:
\be
\item
For safety critical applications, high false alarm rates may be acceptable if the cost
of overlooking any critical can outweigh the inconvenience of having to inspect a few more
modules. 
\item
On the other hand, when rushing a product to market before a competing product is released, there is a business case to 
avoid the extra rework associated with false alarms.  In that business context, 
managers might be willing to lower the recall somewhat in order to minimize the false alarms.
\ee
These two examples are just the tip of the iceberg (see other criteria in \fig{criteria})
and there is insufficient space in this paper to explore all the above optimization goals.
What we can do, however, is show examples of how  changing  optimization goals can also change 
the conclusions made from that learner on that data. Those examples only relate to precision, recall, and the F-measure
but the general principle (that the search bias changes the search conclusions) would hold for all the goals
listed in the previous paragraph.  Hence, we warn that it is important not to overstate  empirical results from software analytics.
Rather, those results need to be expressed {\em along with} the context within which they are
relevant (and by ``context'', we mean the optimization goal).

@@

\begin{figure}[!b]
\begin{center}
\includegraphics[width=1.25in]{precision1.pdf}\includegraphics[width=1.25in]{F1.pdf}
 \end{center}
\caption{Deltas in performance  seen in \fig{precisionbars} (left)
and \fig{fbars} (right) between tuned and untuned learners. Tuning improves performance when the deltas are above zero.}\label{fig:deltas}
 \end{figure}

@@

 \fig{preselect} and \fig{fselect} show the tunings learned by differential evolution. 
The left hand side columns shows some standard default values. Note that:
\bi
\item
The tunings learned by DE
we often very different to the default. That is, to achieve the performance improvements seen in the paper,
the default tuning parameters required a wide range of adjustments.
\item The tunings learned by DE were different in different data sets and for different goals.
That is, to achieve the improvements seen in this paper, tuning has to be repeated whenever the goals or data
sets are changed.
\ei
Given this requirement to repeatedly run tuning, it is fortunate that (as shown above)
tuning is so easy and so fast (at least for defect predictors from static code attributes).
\section{Conclusions}

Prior to this work, our intuition was that tuning would change the behavior or a data miner. Nevertheless, we rarely tuned
since we reasoned:
\bi
\item A data miner's default tunings have been well-explored by the developers of those algorithms. Hence, tuning may rarely improve a data miner.
\item 
Tuning would take so long and be so CPU intensive that the benefits gained   would not be worth effort.
\ei
The results of this paper show that neither of these points is supportable, at least for learning
defect detectors for static code attributes.

Using differential evolution, this paper has found that it is remarkably simple to find effective tunings. We have seen in this paper that:
\bi
\item
Tuning improves the performance scores of a predictor.
That improvement is usually positive (see \fig{deltas} and sometimes
it can be quite   dramatic (precision changing from 2\% to 98\%). 
\item Tuning changes conclusions on what learners are better than others.
Hence, it is time to revisit numerous prior publications of our own~\cite{me07b}
and others~\cite{lessmann2008benchmarking,hall11}.
\item
Tuning changes conclusions about what factors are most important in software development.
Once again, this means that old papers may need to be revised including those
some of our own~\cite{me02k} and others~\cite{bell2013limited,rahman2013how,moser2008comparative,zimmermann2007predicting,herzig2013predicting}. 
\item
Data miners should not be used ``off-the-shelf'' with their default tunings. 
\fig{preselect} and \fig{fselect}    show just how much tuning can alter default settings
both for different data sets and for different goals. Hence, tuning needs to be repeated
whenever data or goals are changed.
\item
Fortunately, the cost of find good tunings is not excessive since, at least for
static code defect predictors, tuning is easy and fast.
\ei
These conclusions need two caveats.
Firstly, the tuning results shown here only came from one  software analytics task 
(defect prediction from static code attributes).
There are many other kinds of software analytics tasks 
(software development effort estimation, social network mining,
detecting duplicate issue reports, etc) and the implication of this
study for those tasks is unclear. 
However,  those other tasks often use the same kinds of learners
explored in this paper so it is quite possible that
the conclusions of this paper apply to other SE analytics tasks as well.

Secondly, it would be incorrect to say that this paper is arguing that
software analytics is somehow wrong-headed, misguided, and we should not do it anymore.
In the age of the Internet and global access to software engineering data,
there exists the  problem of information overload. {\em Something} must be done to
allow analysts to make conclusions via an automatic analysis over a lot of data.
The results of this paper is that for a particular local context
(a specific data set and a specific goal) there exists  
methods for optimizing the conclusions reached in that context.  
Those conclusions
may not generalize to other contexts but this  is not a council for despair. While there may
not exist general conclusions, there does seem to exist general methods for finding
local conclusions in a particular context. Further, as shown above, those
methods may be very simple to implement and very fast to execute.

\section{Future Work}
 This paper has explored  {\em some} learners using {\em one}  optimizer. Hence, we can make
no claim that DE is the {\em best} optimizer for {\em all} learners.
Rather, our point is that there exists at least some learners
whose performance can be dramatically improved by 
at least one simple optimization scheme.  We hope that this work inspires
much future work as this community develops and debugs best practices for tuning
software analytics.

More speculatively,  this notion of using an optimizer to tune
a data miner might need revisiting. As noted by
F\"{u}rnkranz~\cite{furnkranz05}, data mining is inherently a multi-objective optimization
problem that seeks the smallest model with the highest performance, 
that generalizes best for
future examples (perhaps learned in minimal time using the least amount of data).
In this view, we are using DE to optimize an optimizer. Perhaps a better approach might be
to dispense with the separation of ``optimizer'' and ``learner'' and combine them both
into one system that learns how to tune itself as it executes. If this view is useful,
then instead of adding elaborations to data miners (as done in this paper, or by researchers
exploring hyper-heuristics~\cite{jia2013learning}), it should be possible to radically simplify optimization and data
mining with a single system that rapidly performs both task.

>>>>

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{ Analytics Without Parameter Tuning Considered Harmful?}
\numberofauthors{1}
\author{\alignauthor Wei Fu, Tim Menzies \\
       \affaddr{Computer Science, North Carolina State University, Raleigh, USA}\\
       fuwei.ee, tim.menzies@gmail.com}
\maketitle
\begin{abstract}
One of the ``black arts'' of data mining is setting the tuning
parameters that control   choices within a data miner.  We offer a simple,
automatic, and very effective  method for finding those tunings.

@@

One of the ``black arts'' of data mining is setting the tuning
parameters that control  the choices within that data miner.
Many researchers have applied automatic optimizers to find good tunings.
The search-based SE community has   developed techniques
for tuning that treat parameters  as a configuration
search space~\cite{cora10,Krogmann10}. 
The field of {\em hyper-heuristics} explores methods for auto-adapting
options within the device searching for solutions~\cite{jia2013learning} in applications
like test-case generation and code refactorings.
To the best of our knowledge, this paper is the first extensive exploration 
of applying automatic optimizers to tune data miners for defect prediction,
(though see~\cite{cora10,balogh12,Minku13,minku13z} for tuning effort estimators).

Prior to this work, our intuition was that tuning would change the behavior or a data miner, to some degree. Nevertheless, we rarely tuned our  defect predictors 
since we reasoned
that a data miner's default tunings have been well-explored by the developers of those algorithms, in which case
tuning would not lead to large performance improvements.
Also, we suspected that
tuning would take so long and be so CPU intensive that the benefits gained   would not be worth effort.

The results of this paper show that neither of these points is supportable, att least when learning
defect detectors from static code attributes since:
\bi
\item
Tuning static code defect predictors is {\em remarkably simple} and can {\em dramatically improve the performance}
of those learners. 
\ei
Prior to these experiments, our expectation was tuning
would be an  extensive and expensive evolutionary optimization procedure. 
A standard run of such evolutionary optimizers requires   thousands,
if not millions, of evaluations.
To
our surprise, we achieved dramatic improvements in the performance scores
of our data miners after  mere 50 to 80 evaluations (!!) of a very simple evolutionary 
optimizer  called differential evolution~\cite{storn1997differential}.
Better yet,  those  tunings (found so quickly)   
  have a dramatic change to the performance of a learner. For example,
in this paper we show that tuning can alter the precision of
a software defect predictor from 2\% to 98\%.

@@

Thirdly, it is a standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
we have defended that approach on methodological grounds arguing that it
encourages reproducibility~\cite{me15:book1}). That ``off-the-shelf''  policy
can no longer be condoned. For example, suppose our default
number of trees in  a Random Forest was   $F=100$ (which is the default in our implementation). 
Our optimizer settled on  $F$ values that were nowhere near that default:

% {\scriptsize
% \[F \in \left\{\begin{array}{l} 55,  65, 70,   82, 88, 96, 100,  102,  104, 107,\\
%                                 108,  119, 133,  140, 140,   147,  145,  142   \end{array}\right\}
% \]}

{\scriptsize
\[F \in \left\{\begin{array}{l} 50, 59, 63, 63, 69, 71, 81, 85,85, 88,\\
                                92, 95, 96, 99, 99,  100, 104, 106, 107,\\
                                109, 111, 112, 121, 121, 123, 125, 128,\\
                                131, 132, 135, 140, 141, 141, 150   \end{array}\right\}
\]}

@@

Before beginning, we digress for one important clarification.
It would be incorrect to say that this paper is arguing that
software analytics is somehow wrong-headed, misguided, and we should not do it anymore.
In the age of the Internet and global access to software engineering data,
there exists the  problem of information overload. {\em Something} must be done to
allow analysts to make conclusions via an automatic analysis over a lot of data.
The results of this paper is that for a particular local context
(a specific data set and a specific goal) there exists  
methods for optimizing the conclusions reached in that context.  
Those conclusions
may not generalize to other contexts but this  is not a council for despair. While there may
not exist general conclusions, there does seem to exist general methods for finding
local conclusions in a particular context. Further, as shown above, those
methods may be very simple to implement and very fast to execute.

@@

\noindent
We now explore how tuning can change the above  conclusion. Suppose the  predictors $d_1$ and $d_2$  learned from LOC or Halstead
are used to call an inspection
team to check for errors in   parts of the code using:
\begin{equation}\label{eq:yesno}\scriptsize
\mathit{inspect}= \left\{
\begin{array}{ll}
d_i \ge T \rightarrow \mathit{Yes}\\
d_i <   T \rightarrow \mathit{No} 
\end{array}\right.
\end{equation}
\fig{pd1} shows the effects of tuning. Not surprisingly,
at $T=0$, all modules get inspected so the false alarm rate is very high. To reduce that
problem, we can increase $T$. \fig{pd1} reports that the false alarm rate falls below
20\% at $T=0.45$ (for Halstead).

\begin{figure}[!b]

@@

The    lesson from   \fig{pd1}  is that, with tuning, a seemingly poor
detector can work just as well as seemingly better ones.
Note that either the Halstead or LOC detector can reach some desired
level of recall, regardless of their correlations, just by
selecting the appropriate threshold value. For example, in \fig{pd1}, see the recall=75\% values
found at {\em either} $d_i\ge 0.65$ or $d_2\ge 0.45$ (and at the threshold, the false alarm rates
were very similar: 14\% and 19\%).

@@

\section{Experimental Design}\label{sect:design}

@@

For this experiment, we use data sets with at least three  
consecutive releases  (where release $i+1$ was built after release $i$).
\bi 
\item The {\em first} release was used for some  {\em training}, to collect a baseline
   using an untuned learner. This release is also used  on line 24 of Algorithm~\ref{alg:DE} to
   build some model using some the tunings found in some {\em Candidate}.
   \item The {\em second} release was used on 25 of Algorithm~\ref{alg:DE} to 
   test the model found on line 24.
   \item Finally the {\em third} release was used to gather the performance statistics
   reported below from (a)~the model generated by the untuned learner or (b)~the
   best model found by differential evolution.
   \ei
This approach ensures   all treatments 
are assessed on the same tests. Note that we did consider
one other experimental design but rejected it for reasons of
internal validity (see \tion{construct}).

@@

\begin{figure}[!t]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
One style
of measure is to check the {\em variability} of that predictor.
For example,
in their study on reproducibility of SE results,
 Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.

@@

In {\em Better-faster-cheaper},   managers want changes that lead
to fewer defects,  faster development,  using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.

@@

{\scriptsize\[
\begin{array}{ll}
pd=recall=&D/(B+D)\\
pf=&C/(A+C)\\ 
prec=precision=&D/(D+C) \\
F =&2*pd*prec/(pd + prec)
\end{array}
\]}

All the above vary from zero to one. For $pf$, the {\em better} scores are {\em smaller}.
For all other scores, the {\em better} scores are {\em larger}.
One technical detail:   {\em prec}
and {\em F} refer to {\em both} the defect and non-defective modules. This is different to {\em pf} and {\em recall} which only
refer to either non-defective or defective modules (repsectively).

Our analysis results make no assumption that (e.g.) minimizing false alarms is 
more important than maximizing   precision. That determination 
depends on current business conditions:
\be
\item
For safety critical applications, high false alarm rates may be acceptable if the cost
of overlooking any critical can outweigh the inconvenience of having to inspect a few more
modules. 
\item
On the other hand, when rushing a product to market before a competing product is released, there is a business case to 
avoid the extra rework associated with false alarms.  In that business context, 
managers might be willing to lower the recall somewhat in order to minimize the false alarms.
\ee
These two examples are just the tip of the iceberg (see other criteria in \fig{criteria})
and there is insufficient space in this paper to explore all the above optimization goals.
What we can do, however, is show examples of how  changing  optimization goals can also change 
the conclusions made from that learner on that data. Those examples only relate to precision, recall, and the F-measure
but the general principle (that the search bias changes the search conclusions) would hold for all the goals
listed in the previous paragraph.  Hence, we warn that it is important not to overstate  empirical results from software analytics.
Rather, those results need to be expressed {\em along with} the context within which they are
relevant (and by ``context'', we mean the optimization goal).

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=1.25in]{precision1.pdf}\includegraphics[width=1.25in]{F1.pdf}
 \end{center}
\caption{Deltas in performance  seen in \fig{precisionbars} (left)
and \fig{fbars} (right) between tuned and untuned learners. Tuning improves performance when the deltas are above zero.}\label{fig:deltas}
 \end{figure}

@@

 \fig{preselect} and \fig{fselect} show   tunings learned by DE. 
The left hand side columns shows some standard default values. Note that:
\bi
\item
The tunings learned by DE
were often very different to the default. That is, to achieve the performance improvements seen in the paper,
the default tuning parameters required a wide range of adjustments.
\item The tunings learned by DE were different in different data sets and for different goals.
That is, to achieve the improvements seen in this paper, tuning has to be repeated whenever the goals or data
sets are changed.
\ei
Given this requirement to repeatedly run tuning, it is fortunate that (as shown above)
tuning is so easy and so fast (at least for defect predictors from static code attributes).

\section{Reliability and Validity}\label{sect:construct}

{\em Reliability} refers to the consistency of the results obtained
from the research.  For example,   how well independent researchers
could reproduce the study? To increase external
reliability, this paper has taken care to either  clearly define our
algorithms or use implementations from the public domain
(SciKitLearn). Also, all the data used in this work is available
on-line in the PROMISE code repository and all our algorithms
are on-line at github.com/a-se/where.

{\em Validity} refers to the extent to which a piece of research actually
investigates what the researcher purports to investigate.
{\em Internal validity} checks that if the differences found in
the treatments can be ascribed to the treatments under study. 
One internal validity issue with our experiments is the choice
of {\em training, tuning, and testing} data sets discussed in 
\tion{design}. Recall that while all our learners used the same
{\em testing} data set, our untuned learners were only given
access to {\em training} while DEs could get feedback from
{\em training} and
{\em tuning}.  This mean that, potentially,  the performance increases
reported above are merely an artificat of the DEs being able to access
more data. However:
\bi
\item Note that
DEs assess their performance using a model built from {\em training}
then applied to the {\em tuning} data. If we gave the untuned
learners double the training data, then this would be inherently
biased against DEs.
\item In practice, this is much ado about nothing. We have
repeated all the experiments of this paper with the untuned
learners building models from {\em training} + {\em tuning}.
While the exact numbers found in this way
may differ from the above in some small way, we can report that 
those repeated runs do not substantively change the above conclusions.
\ei
{\em External validity} checks if the results are of relevance
for other cases, or can be generalized from samples
to populations.  
The tuning results shown here only came from one  software analytics task 
(defect prediction from static code attributes).
There are many other kinds of software analytics tasks 
(software development effort estimation, social network mining,
detecting duplicate issue reports, etc) and the implication of this
study for those tasks is unclear. 
However,  those other tasks often use the same kinds of learners
explored in this paper so it is quite possible that
the conclusions of this paper apply to other SE analytics tasks as well.

That said, there exist some class of data mining papers for which
tuning may not be required. Consider  Le Goues et al.'s 2012
ICSE paper that used a evolutionary program to learn
repairs to code~\cite{leGoues12}. The performance criteria
in that paper was ``can we fix any of the known bugs?''. Note
that this criteria is a ``{\em competency}'' statement, and
not a ``{\em better than}'' statement (the difference being that
one is 
``can do'' and the other is ``can do better''). For such
competency claims, tuning is not necessary. However, as soon
as {\em better than} enters the performance criteria then this
becomes a race between competing methods. In such a race,
it is unfair to hobble one competitor with poor tunings.

\section{Conclusions}

When learning defect predictors for static code
attributes,   analytics without parameter tuning is considered {\em harmful} and {\em misleading}:
\bi
\item Tuning improves the performance scores of a predictor.
That improvement is usually positive (see \fig{deltas}) and sometimes
it can be quite   dramatic (e.g. precision changing from 2\% to 98\%). \item 
Tuning changes conclusions on what learners are better than others.
Hence, it is time to revisit numerous prior publications of our own~\cite{me07b}
and others~\cite{lessmann2008benchmarking,hall11}.
\item
Tuning changes also changes conclusions on what factors are most important in software development.
Once again, this means that old papers may need to be revised including those
some of our own~\cite{me02k} and others~\cite{bell2013limited,rahman2013how,moser2008comparative,zimmermann2007predicting,herzig2013predicting}. 
\ei
Accordingly, we strongly advise that data miners should not be used ``off-the-shelf'' with their default tunings. 
\fig{preselect} and \fig{fselect}    show just how much tuning can alter default settings
both for different data sets and for different goals.

Since the results from tuning are unstable,
tuning needs to be repeated
whenever data or goals are changed.
Fortunately, the cost of find good tunings is not excessive since, at least for
static code defect predictors, tuning is easy and fast.

As to future work:
\bi
\item
 As noted by
F\"{u}rnkranz~\cite{furnkranz05}, data mining is inherently a multi-objective optimization
problem that seeks the smallest model with the highest performance, 
that generalizes best for
future examples (perhaps learned in minimal time using the least amount of data).
In this view, we are using DE to optimize an optimizer. Perhaps a better approach might be
to dispense with the separation of ``optimizer'' and ``learner'' and combine them both
into one system that learns how to tune itself as it executes. If this view is useful,
then instead of adding elaborations to data miners (as done in this paper, or by researchers
exploring hyper-heuristics~\cite{jia2013learning}), it should be possible to radically simplify optimization and data
mining with a single system that rapidly performs both tasks.
\item
Another issue for future work is the implications of these
conclusions to other kinds of software analytics.
 This paper has explored  {\em some} learners using {\em one}  optimizer. Hence, we can make
no claim that DE is the {\em best} optimizer for {\em all} learners.
Rather, our point is that there exists at least some learners
whose performance can be dramatically improved by 
at least one simple optimization scheme.  We hope that this work inspires
much future work as this community develops and debugs best practices for tuning
software analytics.
\ei
